Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-04 papers/B1555_EdgeOn/B1555_letter.tex
Start of text for Section 2

>>>>

\subsection{Hubble Space Telescope Archival Imaging}

\subsection{Keck Adaptive Optics Imaging}

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A ??x?? cutout of the final reduced image
is shown in Fig.~??b and again in Fig.~??c with contours from the
MERLIN radio observations of \citet{Marlow} overlaid.
